\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-17 Report/project_report.tex
Minor in-text equation reference notation change

\subsection{MSCKF State Covariance Propagation}
With reference to the partitions defined in Equation \ref{eq:covariance}, we compute the predicted camera-camera and IMU-camera state covariances as follows:
\begin{align}
    \hat{\Vec{P}}^-_{CC,k+1} &= \hat{\Vec{P}}_{CC,k} \\
    \hat{\Vec{P}}^-_{IC,k+1} &= \boldsymbol{\Phi}\left(t_k + T, t_k \right) \hat{\Vec{P}}_{IC,k}
\end{align}
where $T$ is the IMU sampling period, and the state transition matrix $\boldsymbol{\Phi}\left(t_k + T, t_k \right)$ is obtained by integrating
\begin{align} \label{eq:statetransition}
    \dot{\boldsymbol{\Phi}}\left(t_k + \tau, t_k \right) &= \Vec{F} \boldsymbol{\Phi}\left(t_k + \tau, t_k \right), \tau\in\left[0,T\right]
\end{align}
with the initial condition $\boldsymbol{\Phi}\left(t_k, t_k \right) = \Vec{1}_{12}$.

@@

If we linearize Equation \ref{eq:residual_def} about the estimates for the camera pose and feature position, we obtain an estimate of the exteroceptive measurement error
\begin{align}
    \Vec{r}_i^{(j)} &\simeq \Vec{H}_{\Vec{x}, i}^{(j)} \widetilde{\Vec{x}}_i + \Vec{H}_{f, i}^{(j)} \widetilde{\Vec{p}}_G^{f_j G} + \Vec{n}_i^{(j)}
\end{align}
where $\Vec{H}_{\Vec{x}, i}^{(j)}$ and $\Vec{H}_{f, i}^{(j)}$ are the Jacobians of the measurement of feature $f_j$ from camera pose $i$ with respect to the filter state and the position of the feature, respectively.
These are given by
\begin{align}
    \Vec{H}_{\Vec{x}, i}^{(j)} &= \bbm \Vec{0} & \Vec{J}^{\left(j\right)}_i \left(\hat{\Vec{p}}_{C_i}^{f_j C_i}\right)^\times & -\Vec{J}^{\left(j\right)}_i \hat{\Vec{C}}_{C_i G} & \Vec{0} \ebm \\
    \Vec{H}_{f, i}^{(j)} &= \Vec{J}^{\left(j\right)}_i \hat{\Vec{C}}_{C_i G}
\end{align}
where the left $\Vec{0}$ in $\Vec{H}_{\Vec{x}, i}^{(j)}$ has dimension $2\times\left(12+6\left(i-1\right)\right)$, the right $\Vec{0}$ has dimension $2\times6\left(N-i\right)$, and
\begin{align}
    \Vec{J}^{\left(j\right)}_i &= \frac{1}{\left(\hat{Z}^{(j)}_{C_i}\right)^2}
    \bbm \hat{Z}^{(j)}_{C_i} & 0 & -\hat{X}^{(j)}_{C_i} \vspace{0.5em} \\
             0 & \hat{Z}^{(j)}_{C_i} & -\hat{Y}^{(j)}_{C_i}
    \ebm .
\end{align}
$\Vec{n}_i^{(j)}$ is a zero-mean Gaussian noise term with covariance matrix $\Vec{R}_i^{(j)} = \sigma^2_{\text{im}} \Vec{1}_{2}$.

@@

We can now stack all the errors $\Vec{r}_o^{(j)}$ for all the features in the current batch to arrive at
\begin{align} \label{eq:residual_nullspace_stacked}
    \Vec{r}_o &= \Vec{H}_o \widetilde{\Vec{x}} + \Vec{n}_o .
\end{align}
The dimension of this vector can be quite large in practice, so we use the QR-decomposition of $\Vec{H}_o$ to reduce the computational complexity of the EKF update:
\begin{align}
    \Vec{H}_o = \bbm \Vec{Q}_1 & \Vec{Q}_2 \ebm \bbm \Vec{T}_\Vec{H} \\ \Vec{0} \ebm
\end{align}
where $\Vec{Q}_1, \Vec{Q}_2$ are unitary matrices and $\Vec{T}_\Vec{H}$ is an upper-triangular matrix.
Substituting this result into Equation \ref{eq:residual_nullspace_stacked} and pre-multiplying by $\bbm \Vec{Q}_1 & \Vec{Q}_2 \ebm ^T$, we obtain
\begin{align}
    \bbm \Vec{Q}_1^T \Vec{r}_o \\ \Vec{Q}_2^T \Vec{r}_o \ebm &= \bbm \Vec{T}_\Vec{H} \\ \Vec{0} \ebm \widetilde{\Vec{x}} + \bbm \Vec{Q}_1^T \Vec{n}_o \\ \Vec{Q}_2^T \Vec{n}_o \ebm .
\end{align}
Noting that the quantity $\Vec{Q}_2^T \Vec{r}_o$ is only noise, we discard it and define a new error term that we use in the EKF update:
\begin{align}
    \Vec{r}_n &:= \Vec{Q}_1^T \Vec{r}_o = \Vec{T}_\Vec{H} \widetilde{\Vec{x}} + \Vec{Q}_1^T \Vec{n}_o =: \Vec{T}_\Vec{H} \widetilde{\Vec{x}} + \Vec{n}_n
\end{align} 
The covariance matrix of $\Vec{n}_n$ is given by $\Vec{R}_n = \Vec{Q}_1^T \Vec{R}_o \Vec{Q}_1 = \sigma^2_\text{im} \Vec{1}_r$ where $r$ is the number of columns in $\Vec{Q}_1$.

>>>>

\subsection{MSCKF State Covariance Propagation}
With reference to the partitions defined in (\ref{eq:covariance}), we compute the predicted camera-camera and IMU-camera state covariances as follows:
\begin{align}
    \hat{\Vec{P}}^-_{CC,k+1} &= \hat{\Vec{P}}_{CC,k} \\
    \hat{\Vec{P}}^-_{IC,k+1} &= \boldsymbol{\Phi}\left(t_k + T, t_k \right) \hat{\Vec{P}}_{IC,k}
\end{align}
where $T$ is the IMU sampling period, and the state transition matrix $\boldsymbol{\Phi}\left(t_k + T, t_k \right)$ is obtained by integrating
\begin{align} \label{eq:statetransition}
    \dot{\boldsymbol{\Phi}}\left(t_k + \tau, t_k \right) &= \Vec{F} \boldsymbol{\Phi}\left(t_k + \tau, t_k \right), \tau\in\left[0,T\right]
\end{align}
with the initial condition $\boldsymbol{\Phi}\left(t_k, t_k \right) = \Vec{1}_{12}$.

@@

If we linearize (\ref{eq:residual_def}) about the estimates for the camera pose and feature position, we obtain an estimate of the exteroceptive measurement error
\begin{align}
    \Vec{r}_i^{(j)} &\simeq \Vec{H}_{\Vec{x}, i}^{(j)} \widetilde{\Vec{x}}_i + \Vec{H}_{f, i}^{(j)} \widetilde{\Vec{p}}_G^{f_j G} + \Vec{n}_i^{(j)}
\end{align}
where $\Vec{H}_{\Vec{x}, i}^{(j)}$ and $\Vec{H}_{f, i}^{(j)}$ are the Jacobians of the measurement of feature $f_j$ from camera pose $i$ with respect to the filter state and the position of the feature, respectively.
These are given by
\begin{align}
    \Vec{H}_{\Vec{x}, i}^{(j)} &= \bbm \Vec{0} & \Vec{J}^{\left(j\right)}_i \left(\hat{\Vec{p}}_{C_i}^{f_j C_i}\right)^\times & -\Vec{J}^{\left(j\right)}_i \hat{\Vec{C}}_{C_i G} & \Vec{0} \ebm \\
    \Vec{H}_{f, i}^{(j)} &= \Vec{J}^{\left(j\right)}_i \hat{\Vec{C}}_{C_i G}
\end{align}
where the left $\Vec{0}$ in $\Vec{H}_{\Vec{x}, i}^{(j)}$ has dimension $2\times\left(12+6\left(i-1\right)\right)$, the right $\Vec{0}$ has dimension $2\times6\left(N-i\right)$, and
\begin{align}
    \Vec{J}^{\left(j\right)}_i &= \frac{1}{\left(\hat{Z}^{(j)}_{C_i}\right)^2}
    \bbm \hat{Z}^{(j)}_{C_i} & 0 & -\hat{X}^{(j)}_{C_i} \vspace{0.5em} \\
             0 & \hat{Z}^{(j)}_{C_i} & -\hat{Y}^{(j)}_{C_i}
    \ebm .
\end{align}
$\Vec{n}_i^{(j)}$ is a zero-mean Gaussian noise term with covariance matrix $\Vec{R}_i^{(j)} = \sigma^2_{\text{im}} \Vec{1}_{2}$.

@@

We can now stack all the errors $\Vec{r}_o^{(j)}$ for all the features in the current batch to arrive at
\begin{align} \label{eq:residual_nullspace_stacked}
    \Vec{r}_o &= \Vec{H}_o \widetilde{\Vec{x}} + \Vec{n}_o .
\end{align}
The dimension of this vector can be quite large in practice, so we use the QR-decomposition of $\Vec{H}_o$ to reduce the computational complexity of the EKF update:
\begin{align}
    \Vec{H}_o = \bbm \Vec{Q}_1 & \Vec{Q}_2 \ebm \bbm \Vec{T}_\Vec{H} \\ \Vec{0} \ebm
\end{align}
where $\Vec{Q}_1, \Vec{Q}_2$ are unitary matrices and $\Vec{T}_\Vec{H}$ is an upper-triangular matrix.
Substituting this result into (\ref{eq:residual_nullspace_stacked}) and pre-multiplying by $\bbm \Vec{Q}_1 & \Vec{Q}_2 \ebm ^T$, we obtain
\begin{align}
    \bbm \Vec{Q}_1^T \Vec{r}_o \\ \Vec{Q}_2^T \Vec{r}_o \ebm &= \bbm \Vec{T}_\Vec{H} \\ \Vec{0} \ebm \widetilde{\Vec{x}} + \bbm \Vec{Q}_1^T \Vec{n}_o \\ \Vec{Q}_2^T \Vec{n}_o \ebm .
\end{align}
Noting that the quantity $\Vec{Q}_2^T \Vec{r}_o$ is only noise, we discard it and define a new error term that we use in the EKF update:
\begin{align}
    \Vec{r}_n &:= \Vec{Q}_1^T \Vec{r}_o = \Vec{T}_\Vec{H} \widetilde{\Vec{x}} + \Vec{Q}_1^T \Vec{n}_o =: \Vec{T}_\Vec{H} \widetilde{\Vec{x}} + \Vec{n}_n
\end{align} 
The covariance matrix of $\Vec{n}_n$ is given by $\Vec{R}_n = \Vec{Q}_1^T \Vec{R}_o \Vec{Q}_1 = \sigma^2_\text{im} \Vec{1}_r$ where $r$ is the number of columns in $\Vec{Q}_1$.
